On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-01 tt_intro.tex
S.S. commit before dinner
I'm still working on the intro for TTT.

At delay 1, a bead cannot collaborate with its successors in order to stabilize itself. 
In fact, there are just two ways for a bead to get stabilized at delay 1 (or the bead has no place to be stabilized around so that the system halts). 
One is to be bound and the other is through a 1-in-1-out structure called the tunnel section. 
See Fig.~\ref{fig:TTT_tunnel}. 
A \textit{tunnel section} consists of four beads that occupy four neighbors of one point.

Let us consider the stabilization of the $i$-th bead $w[i]$ of the transcript $w$ upon $C_{i-1}$. 
The bead cannot collaborate with any succeeding bead $w[i+1],w[i+2],\cdots$ at delay 1. There are just two ways to get stabilized at delay 1. One way is to be bound to another bead. The other way is through a $tunnel\ section$. A tunnel section consists of four beads that occupy four neighbors of a point (Fig.\ref{TTT_tunnel_intro}). 
Accordingly, how they are stabilized can be described by a sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section. 
We let $S$ take the value $\blacksquare$ for halt.

@@

We say that point $p$ is reachable from a conformation $C$ if there exists a directed path $P^\prime$ from the last point of $C$ that does not cross the path of $C$. We define $binding\ capability$ with reachable.

>>>>

At delay 1, a bead cannot collaborate with its successors in order to stabilize itself. 
In fact, there are just two ways for a bead to get stabilized at delay 1 (or the bead has no place to be stabilized around so that the system halts). 
One is to be bound and the other is through a 1-in-1-out structure called the tunnel section. 
See Fig.~\ref{fig:TTT_tunnel}. 
A \textit{tunnel section} consists of four beads that occupy four neighbors of one free point. 
The behavior of a deterministic oritatami system at delay 1 can be described by a sequence of $S$ of $b$ (bound), $t_s$ (straight tunnel section), $t_o$ (obtuse-turn tunnel section), and $t_a$ (acute-turn tunnel section); priority is given to tunnel, that is, $S[i]$ is $t_s$ (resp.~$t_o$, $t_a$) if the $i$-th bead of the system is stabilized not only by being bonded but also through a straight (resp. obtuse-turn, acute-turn) tunnel section. 
We let $S$ take the value $\blacksquare$ for halt (due to the lack of free neighbors).

@@

We say that point $p$ is reachable from a conformation $C$ if there exists a directed path $P^\prime$ from the last point of $C$ that does not cross the path of $C$. 
Taking this reachability into account, we define the \textit{binding capability} of a conformation as the number of free bonds of its beads available geometrically for elongations of $C$.
It is defined formally as follows:
